The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-21 Paper.Rmd
modify table...continued

```{r tab_bivar_summary, echo=F, results='markup'}

tab_bivar_summary<-readRDS("./Results/tab_bivar_summary.RDS")
knitr::kable(tab_bivar_summary, 
             format='pandoc',
             caption = "Summary of results for bivariate data-sets : \\textbf{p.Independence.test}: p-value from `BiCopIndTest`, \\textbf{minimumAIC.bestfit.copula}: best fit copula based on minimum AIC, \\textbf{Bestfit.copula.AICw}: AIC-weight of that best fit copula, \\textbf{Normal.copula.AICw}: AIC-weight of Normal copula, \\textbf{p.CvM}: p-value from `BiCopGofTest` for Cramer-von Mises method, \\textbf{p.KS}: p-value from `BiCopGofTest` for Kolmogorov-Smirnov method,\\textbf{LT.model.avg}: AIC-weights model averaged lower tail dependence, \\textbf{UT.model.avg}: AIC-weights model averaged upper tail dependence, \\textbf{(LT-UT).model.avg}:  AIC-weights model averaged (lower-upper) tail dependence. Statistic $\\Ps_l$ - $\\Ps_u$ for the actual copula data and for Kendall-correlation preserving $1000$ Normal surrogates were computed and ranked in ascending order. Rank for real data \\textbf{Rank.(Pl-Pu)}, if were $>975$ or $<25$, then indicated a significantly ($95\\%$ CI) different lower or upper tail-dependent measures based on Normal-null hypothesis.
\\label{tab_bivar_summary}",
             booktabs=TRUE)
```

@@

tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
knitr::kable(tab_multivar_summary, 
             format='pandoc',
             caption = "Summary of results for multivariate data-sets : \\textbf{num.pairs}: total number of location pairs (excluding self-comparison) considered, \\textbf{num.non-indep}: how many location pair copula are non-independent among them, \\textbf{num.non-N}: number of non-Normal copula as best fit (based on highest AIC-weight), \\textbf{Avg.best.AICw}: average AIC-weights of best fit copula from all location pair, \\textbf{Avg.N.AICw}: average AIC-weights of Normal copula from all location pair, \\textbf{num.good.fit}: number of location pair for which best fit copula have p-values $>$ 0.01 
(both Cramer-von Mises and Kolmogorov-Smirnov method), \\textbf{0.025-CI.LT}: lower and \\textbf{0.975-CI.LT}: upper quantile ($95\\%$CI) of model averaged (AIC-weight based) lower tail dependence from all location pair, \\textbf{0.025-CI.UT}: lower and \\textbf{0.975-CI.UT}: upper quantile ($95\\%$CI) of model averaged (AIC-weight based) upper tail dependence from all location pair, \\textbf{num.LT-UT>0}: number of location pair which showed stronger lower tail dependence than upper, Last $6$ rows summarized the non-parametric analysis results for $\\Ps$ statistics : lower and upper quantile ($95\\%$CI) of $\\Ps_l$, $\\Ps_u$, $\\Ps_l-\\Ps_u$ based on resampling location pair.\\label{tab_multivar_summary}",
             booktabs=TRUE)
```

@@

>>>>

<!--
```{r tab_bivar_summary, echo=F, results='markup'}
tab_bivar_summary<-readRDS("./Results/tab_bivar_summary.RDS")
knitr::kable(tab_bivar_summary, 
             format='pandoc',
             caption = "Summary of results for bivariate data-sets : \\textbf{p.Independence.test}: p-value from `BiCopIndTest`, \\textbf{minimumAIC.bestfit.copula}: best fit copula based on minimum AIC, \\textbf{Bestfit.copula.AICw}: AIC-weight of that best fit copula, \\textbf{Normal.copula.AICw}: AIC-weight of Normal copula, \\textbf{p.CvM}: p-value from `BiCopGofTest` for Cramer-von Mises method, \\textbf{p.KS}: p-value from `BiCopGofTest` for Kolmogorov-Smirnov method,\\textbf{LT.model.avg}: AIC-weights model averaged lower tail dependence, \\textbf{UT.model.avg}: AIC-weights model averaged upper tail dependence, \\textbf{(LT-UT).model.avg}:  AIC-weights model averaged (lower-upper) tail dependence. Statistic $\\Ps_l$ - $\\Ps_u$ for the actual copula data and for Kendall-correlation preserving $1000$ Normal surrogates were computed and ranked in ascending order. Rank for real data \\textbf{Rank.(Pl-Pu)}, if were $>975$ or $<25$, then indicated a significantly ($95\\%$ CI) different lower or upper tail-dependent measures based on Normal-null hypothesis.
\\label{tab_bivar_summary}",
             booktabs=TRUE)
```

@@

tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
knitr::kable(tab_multivar_summary, 
             format='pandoc',
             caption = "Summary of results for multivariate data-sets : \\textbf{num.pairs}: total number of location pairs (excluding self-comparison) considered, \\textbf{num.non-indep}: how many location pair copula are non-independent among them, \\textbf{num.non-N}: number of non-Normal copula as best fit (based on highest AIC-weight), \\textbf{Avg.best.AICw}: average AIC-weights of best fit copula from all location pair, \\textbf{Avg.N.AICw}: average AIC-weights of Normal copula from all location pair, \\textbf{num.good.fit}: number of location pair for which best fit copula have p-values $>$ 0.01 
(both Cramer-von Mises and Kolmogorov-Smirnov method), \\textbf{0.025-CI.LT}: lower and \\textbf{0.975-CI.LT}: upper quantile ($95\\%$CI) of model averaged (AIC-weight based) lower tail dependence from all location pair, \\textbf{0.025-CI.UT}: lower and \\textbf{0.975-CI.UT}: upper quantile ($95\\%$CI) of model averaged (AIC-weight based) upper tail dependence from all location pair, \\textbf{num.LT-UT>0}: number of location pair which showed stronger lower tail dependence than upper, Last $6$ rows summarized the non-parametric analysis results for $\\Ps$ statistics : lower and upper quantile ($95\\%$CI) of $\\Ps_l$, $\\Ps_u$, $\\Ps_l-\\Ps_u$ based on resampling location pair.\\label{tab_multivar_summary}",
             booktabs=TRUE)
```
-->

<!--bivariate table summary in latex format-->
```{r tab_bivar_summaryl, echo=F, results='asis',message=F}
tab_bivar_summary<-readRDS("./Results/tab_bivar_summary.RDS")
row.names(tab_bivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(Description = c("1. p-value from independence test",
           "2. best fit copula based on minimum AIC",
           "3. AIC-weight of that best fit copula",
           "4. AIC-weight of Normal copula",
           "5. p-value from goodness of fit test for Cramer-von Mises method",
           "6. p-value from goodness of fit test for Kolmogorov-Smirnov method",
           "7. model averaged (AIC-weights based) lower tail dependence",
           "8. model averaged (AIC-weights based) upper tail dependence",
           "9. model averaged (AIC-weights based) (lower - upper) tail dependence",
           "10. Rank of statistics (Pl-Pu) for real data in comparison to 1000 Normal surrogates")
)
tab_bivar_summary<-cbind(dt,tab_bivar_summary)
knitr::kable(tab_bivar_summary, 
             format="latex", 
             caption = "Summary of results for bivariate data-sets\\label{tab_bivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ", "SoilCN", "Birds’ BMR", "Mammals’ BMR", "Ceder-creek")
             )%>%column_spec(2:5,width="1.4cm")%>%
             column_spec(1, width = "11cm")%>%kable_styling(latex_options = "basic",position = "center")
```

<!--multivariate table summary in latex format-->

```{r tab_multivar_summaryl, echo=F, results='asis',message=F}
tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
tab_multivar_summary<-tab_multivar_summary[c(1:11,16,17),]
row.names(tab_multivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
#Items = c("num.pairs","num.non-indep", "num.non-N", "Avg.best.AICw", "Avg.N.AICw", "num.good.fit", "0.025-CI.LT",
#          "0.975-CI.LT","0.025-CI.UT","0.975-CI.UT","num.LT-UT>0","0.025-CI.Pl-Pu","0.975-CI.Pl-Pu"),
Description = c("1. total number of location pairs (excluding self-comparison)",
           "2. how many location pair have non-independent copula structures",
           "3. number of non-Normal copula as best fit",
           "4. average AIC-weights of best fit copula from all location pair",
           "5. average AIC-weights of Normal copula from all location pair",
           "6. number of location pair having best fit copula with p-values > 0.01
            (both Cramer-von Mises and Kolmogorov-Smirnov method)",
           "7. 2.5 percentile of model-avg. lower tail-dep. from all location pair",
           "8. 97.5 percentile of model-avg. lower tail-dep. from all location pair",
           "9. 2.5 percentile of model-avg. upper tail-dep. from all location pair",
           "10. 97.5 percentile of model-avg. upper tail-dep. from all location pair",
           "11. number of location pair showing stronger lower tail dependence",
           "12. 2.5 percentile of Pl-Pu statistics from all location pair",
           "13. 97.5 percentile of Pl-Pu statistics from all location pair")
)

tab_multivar_summary<-cbind(dt,tab_multivar_summary)
knitr::kable(tab_multivar_summary, 
             format="latex", 
             caption = "Summary of results for multivariate data-sets\\label{tab_multivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ","Green-spruce aphid count",
                        "Leaf-plum curling aphid firstflight",
                        "Ceratium furca count","Methane-flux")
             )%>%column_spec(2:5,width="1.4cm")%>%
             column_spec(1, width = "11cm")%>%kable_styling(latex_options = "basic",position = "center")
```

@@

<!--what we did?-->
In the earlier work, most of the studies in ecology focused on measuring correlations between variables and thus ignoring the possibility to recognize importance of asymmetric tail-dependence and non-Normal copulae in this field. We

<!--why is it important to study?-->

<!--future work-->
